### 2014-08-04 paper/paper.tex
Wrote a readme in preperation of making this repo public
Wrote a whole bunch more for the background. Included an example tweet in the dataset

The focus of this undergraduate research project has been to preform sentiment
analysis in data from the microbloging website Twitter. All of the messages,
known as Tweets, are constrained in length to 140 characters. This limit forces
many users of Twitter to use abbreviations and contractions. This data presents
some interesting problems to performing good sentiment analysis due to it's
short and informal nature. Twitter makes it extremely easy to publish a Tweet
and has no way to edit a Tweet once published. This results in more spelling
mistakes and inconsistent grammar then other sources of text. Tweets often also
contain URLs to other websites. Tweets also contain a certain amount of OOV
(Out-Of-Vocabulary) words, such as Hashtags, a tagging system for topics
allowing Tweets in a similar vein of conversation to be found. Other OOV words
include mentions (e.g. `@BarackObama') which are a method to direct a tweet to
one or more users, as well as `RT' which is an acronym for `retweet'
communicating that this particular Tweet is a reissuing of another users Tweet.
Another issue that is out of the scope of this project is that Twitter
currently supports 35+ languages, meaning that in-order to determine the
sentiment most systems must first determine which language the tweet is in.

@@

Quite a bit of research has been done in the field of sentiment analysis
recently. Much of the work has involved data from other contexts such as Movie
reviews \cite{Pang2002}, and blog posts \cite{Melville2009}. The challenges
associated with classifying Twitter data has attracted researchers in the past
few years \cite{Jianfeng2013} \cite{Barbosa2010} \cite{Gokulakrishnan2012}.
Sentiment analysis has been very closely linked with opinion mining, which is
the practice of extracting sentiment on a particular topic in order to gain
insights into public opinion on the topic.

According to `Opinion mining and sentiment analysis' \cite{Pang2008}: ``The
year 2001 or so seems to mark the beginning of widespread awareness of the
research problems that sentiment analysis and opinion mining raise''. This
explosion in research has happened very recently, and as such the field is
moving very quickly.

Many previous attempts researched make use of Naive Bayes, Maximum Entropy, and
SVM classifiers. The Naive Bayes classifier uses the occurrences of features in
the \textit{training set} to calculate the probability that an example in the
\textit{test set} belongs in a given class. This method has the benefit of
linear time training since there is no iterative process, but I makes the
assumption that all features are independent, which is not the case in natural
language. The Maximum Entropy approach is explained in detail in section
\ref{ssection:summaryofmaxent}.

%TODO Sentiment Analysis
%TODO Text Classification
%TODO Feature Selection

@@

The dataset for the task consists of 6225 labelled Tweets. 36.66\% of the
corpus has `positive' label, 14.04\% has a `negative' label, 49.30\% has a
label that conveys neutral sentiment. This neutral label is one of `neutral',
`objective', or `objective-OR-neutral'.

%TODO add example

@@

Nearly all Twitter users have published more than one tweet. A more advanced
classifier could establish a particular users propensity to publishing a
prevailing sentiment in all of their tweets.

As well, some Twitter users may be frequently be referred to with a particular
sentiment. For a hypothetical example, Tweets addressed to Emma Watson
(`@EmWatson') are more likely to have a positive sentiment, while tweets to
Barack Obama (`@BarackObama') may contain extremely mixed sentiment.

@@

\begin{Verbatim}[fontsize=\footnotesize]
wget https://github.com/hockeybuggy/semantic_eval/archive/master.zip
unzip master.zip
cd master
\end{Verbatim}
% TODO test this and make a dist branch

>>>>

The focus of this undergraduate research project has been to preform sentiment
analysis in data from the microbloging website Twitter. All of the messages,
known as Tweets, are constrained in length to 140 characters. This limit forces
many users of Twitter to use abbreviations and contractions. This data presents
some interesting problems to performing good sentiment analysis due to it's
short and informal nature. Twitter makes it extremely easy to publish a Tweet
and has no way to edit a Tweet once published. This results in more spelling
mistakes and inconsistent grammar then other sources of text. Tweets often also
contain URLs to other websites. Tweets also contain a certain amount of OOV
(Out-Of-Vocabulary) words, such as Hashtags, a tagging system for topics
allowing Tweets in a similar vein of conversation to be found. Other OOV words
include mentions (e.g. `@BarackObama') which are a method to direct a Tweet to
one or more users, as well as `RT' which is an acronym for `retweet'
communicating that this particular Tweet is a reissuing of another users Tweet.
Another issue that is out of the scope of this project is that Twitter
currently supports 35+ languages, meaning that in-order to determine the
sentiment most systems must first determine which language the Tweet is in.

@@

According to `Opinion Mining and Sentiment Analysis' \cite{Pang2008}: ``The
year 2001 or so seems to mark the beginning of widespread awareness of the
research problems that sentiment analysis and opinion mining raise''. This
explosion in research has happened very recently, and as such the field is
moving very quickly. Much of the earlier work in the field involved data from
other contexts such as Movie reviews \cite{Pang2002}, and blog posts
\cite{Melville2009}. The challenges associated with classifying Twitter data
has only attracted researchers in the past few years \cite{Jianfeng2013}
\cite{Barbosa2010} \cite{Gokulakrishnan2012}.

Sentiment analysis is a very specific type of \textbf{text classification}, a problem
that is well summarized in chapter 6 of \textit{Mining Text Data} by Aggarwal
and Zhai \cite{Aggarwal2012} as:

\begin{quote}
    We have a set of training records $\mathcal{D} = \{X_{1} , . . .\ , X_{N}
    \}$, such that each record is labeled with a class value drawn from a set
    of k different discrete values indexed by $\{1 . . . k\}$. The training
    data is used in order to construct a classification model, which relates
    the features in the underlying record to one of the class labels.
\end{quote}

In the case of sentiment analysis the class labels being applied to the records
denote the attitude or opinion in the text. The focus of this project is
determining sentiment at the document level which assumes that the document
expresses a predominate sentiment. This is a somewhat reasonable assumption
given the fact that Tweets are limited in size, making it difficult to express
mixed sentiment. Sentiment analysis is very closely linked with opinion mining,
which is the practice of extracting sentiment on a particular topic in order to
gain insights into public opinion on the topic.

Much of the previous research make use of Naive Bayes, Maximum Entropy, and
SVM classifiers. The Naive Bayes classifier uses the occurrences of features in
the \textit{training set} to calculate the probability that an example in the
\textit{test set} belongs in a given class. This method has the benefit of
linear time training since there is no iterative process, but I makes the
assumption that all features are independent, which is not the case in natural
language. The Maximum Entropy approach is explained in detail in section
\ref{ssection:summaryofmaxent}. While Maximum Entropy and Naive Bayes are both
probabilistic approaches the to problem, Support Vector Machine (SVM)
classifiers take a different approach to the problem. ``SVM Classifiers attempt
partition the data space with the use of linear or non-linear delineations
between the different classifiers.''\cite{Aggarwal2012}.

%TODO Feature Selection

@@

The dataset for the task consists of 6225 labelled Tweets. 36.66\% of the
corpus has `positive' label, 14.04\% has a `negative' label, 49.30\% has a
label that conveys neutral sentiment. This neutral label is one of `neutral',
`objective', or `objective-OR-neutral'. The following is an example of a
positive Tweet:

\begin{Verbatim}[fontsize=\footnotesize]
"positive", "Gas by my house hit $3.39!!!! I'm going to Chapel Hill on Sat. :)"
\end{Verbatim}

@@

Nearly all Twitter users have published more than one Tweet. A more advanced
classifier could establish a particular users propensity to publishing a
prevailing sentiment in all of their Tweets.

As well, some Twitter users may be frequently be referred to with a particular
sentiment. For a hypothetical example, Tweets addressed to Emma Watson
(`@EmWatson') are more likely to have a positive sentiment, while Tweets to
Barack Obama (`@BarackObama') may contain extremely mixed sentiment.

@@

\begin{Verbatim}[fontsize=\footnotesize]
wget https://github.com/hockeybuggy/semantic_eval/archive/master.zip
unzip master.zip
cd master
\end{Verbatim}

% TODO test this and make a dist branch
